### 2022-12-31 output/summary_statistics/tables/balance_table.tex
Added median to summary statistics

\begin{tabular}{llcccc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Cases Won by Defendant}} & \multicolumn{2}{c}{\textit{Cases Won by Plaintiff}} \\
 &  & Mean & N & Mean & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 4082 & 0.12 & 11912 \\
 & For cause (transfer) & 0.01 & 4082 & 0.01 & 11912 \\
 & Foreclosure & 0.01 & 4082 & 0.03 & 11912 \\
 & Foreclosure (transfer) & 0.00 & 4082 & 0.00 & 11912 \\
 & No cause & 0.12 & 4082 & 0.10 & 11912 \\
 & No cause (transfer) & 0.01 & 4082 & 0.00 & 11912 \\
 & Non-payment of rent & 0.69 & 4082 & 0.72 & 11912 \\
 & Non-payment of rent (transfer) & 0.03 & 4082 & 0.01 & 11912 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 97.63 & 4082 & 58.85 & 10273 \\
 & Case defaulted & 0.00 & 4082 & 0.67 & 11912 \\
 & Case involuntarily dismissed & 0.99 & 4082 & 0.00 & 11912 \\
 & Case heard & 0.01 & 4082 & 0.19 & 11912 \\
 & Case mediated & 0.00 & 4082 & 0.00 & 11912 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.20 & 4082 & 0.07 & 11912 \\
 & Plaintiff has an attorney & 0.79 & 4082 & 0.81 & 11912 \\
 & Defendant is an entity & 0.01 & 4082 & 0.01 & 11912 \\
 & Plaintiff is an entity & 0.63 & 4082 & 0.67 & 11912 \\
 & Money judgment & 57.67 & 4082 & 3440.73 & 11912 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 1256 & 8997593.33 & 3991 \\
 & Building value & 1605427.57 & 1256 & 2352903.60 & 3991 \\
 & Land value & 61247.49 & 1256 & 101018.42 & 3991 \\
 & Other value & 8138231.73 & 1256 & 11440367.23 & 3991 \\
 & Units & 41.23 & 1256 & 42.10 & 3991 \\
\cline{1-6}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 255719.80 & 1018 & 267442.86 & 2901 \\
 & Four years before latest docket date & 278556.70 & 1034 & 285983.57 & 2936 \\
 & Three years before latest docket date & 297696.16 & 1051 & 312711.10 & 3012 \\
 & Two years before latest docket date & 332887.98 & 1054 & 339939.67 & 3013 \\
 & One year before latest docket date & 338734.41 & 1057 & 359532.30 & 3015 \\
 & Latest docket date & 373978.71 & 1043 & 385699.20 & 2990 \\
 & One year after latest docket date & 419565.10 & 1085 & 431037.20 & 3084 \\
 & Two years after latest docket date & 446321.14 & 823 & 490315.74 & 2723 \\
 & Three years after latest docket date & 482787.35 & 454 & 507050.53 & 1791 \\
\cline{1-6}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcccc}
\toprule
 &  & \multicolumn{3}{c}{\textit{Cases Won by Defendant}} & \multicolumn{3}{c}{\textit{Cases Won by Plaintiff}} \\
 &  & Median & Mean & N & Median & Mean & N \\
Panel & Variable &  &  &  &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.00 & 0.12 & 4082 & 0.00 & 0.12 & 11912 \\
 & For cause (transfer) & 0.00 & 0.01 & 4082 & 0.00 & 0.01 & 11912 \\
 & Foreclosure & 0.00 & 0.01 & 4082 & 0.00 & 0.03 & 11912 \\
 & Foreclosure (transfer) & 0.00 & 0.00 & 4082 & 0.00 & 0.00 & 11912 \\
 & No cause & 0.00 & 0.12 & 4082 & 0.00 & 0.10 & 11912 \\
 & No cause (transfer) & 0.00 & 0.01 & 4082 & 0.00 & 0.00 & 11912 \\
 & Non-payment of rent & 1.00 & 0.69 & 4082 & 1.00 & 0.72 & 11912 \\
 & Non-payment of rent (transfer) & 0.00 & 0.03 & 4082 & 0.00 & 0.01 & 11912 \\
\cline{1-8}
\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 61.00 & 97.63 & 4082 & 20.00 & 58.85 & 10273 \\
 & Case defaulted & 0.00 & 0.00 & 4082 & 1.00 & 0.67 & 11912 \\
 & Case involuntarily dismissed & 1.00 & 0.99 & 4082 & 0.00 & 0.00 & 11912 \\
 & Case heard & 0.00 & 0.01 & 4082 & 0.00 & 0.19 & 11912 \\
 & Case mediated & 0.00 & 0.00 & 4082 & 0.00 & 0.00 & 11912 \\
\cline{1-8}
\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.00 & 0.20 & 4082 & 0.00 & 0.07 & 11912 \\
 & Plaintiff has an attorney & 1.00 & 0.79 & 4082 & 1.00 & 0.81 & 11912 \\
 & Defendant is an entity & 0.00 & 0.01 & 4082 & 0.00 & 0.01 & 11912 \\
 & Plaintiff is an entity & 1.00 & 0.63 & 4082 & 1.00 & 0.67 & 11912 \\
 & Money judgment & 0.00 & 57.67 & 4082 & 1310.94 & 3440.73 & 11912 \\
\cline{1-8}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 641200.00 & 6478531.48 & 1256 & 579400.00 & 8997593.33 & 3991 \\
 & Building value & 169600.00 & 1605427.57 & 1256 & 161000.00 & 2352903.60 & 3991 \\
 & Land value & 1100.00 & 61247.49 & 1256 & 2100.00 & 101018.42 & 3991 \\
 & Other value & 823450.00 & 8138231.73 & 1256 & 808100.00 & 11440367.23 & 3991 \\
 & Units & 2.00 & 41.23 & 1256 & 1.00 & 42.10 & 3991 \\
\cline{1-8}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 185330.50 & 255719.80 & 1018 & 218825.00 & 267442.86 & 2901 \\
 & Four years before latest docket date & 195892.50 & 278556.70 & 1034 & 228526.00 & 285983.57 & 2936 \\
 & Three years before latest docket date & 210030.00 & 297696.16 & 1051 & 244821.50 & 312711.10 & 3012 \\
 & Two years before latest docket date & 223501.00 & 332887.98 & 1054 & 264659.00 & 339939.67 & 3013 \\
 & One year before latest docket date & 240000.00 & 338734.41 & 1057 & 285032.00 & 359532.30 & 3015 \\
 & Latest docket date & 270184.00 & 373978.71 & 1043 & 313104.50 & 385699.20 & 2990 \\
 & One year after latest docket date & 317500.00 & 419565.10 & 1085 & 354320.00 & 431037.20 & 3084 \\
 & Two years after latest docket date & 348300.00 & 446321.14 & 823 & 404600.00 & 490315.74 & 2723 \\
 & Three years after latest docket date & 363650.00 & 482787.35 & 454 & 419600.00 & 507050.53 & 1791 \\
\cline{1-8}
\bottomrule
\end{tabular}

### 2022-12-31 output/summary_statistics/tables/summary_statistics.tex
Added median to summary statistics

\begin{tabular}{llccc}
\toprule
 &  & Mean & S.D. & N \\
Panel & Variable &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.32 & 40,727 \\
 & For cause (transfer) & 0.01 & 0.08 & 40,727 \\
 & Foreclosure & 0.02 & 0.14 & 40,727 \\
 & Foreclosure (transfer) & 0.00 & 0.03 & 40,727 \\
 & No cause & 0.10 & 0.30 & 40,727 \\
 & No cause (transfer) & 0.01 & 0.08 & 40,727 \\
 & Non-payment of rent & 0.73 & 0.44 & 40,727 \\
 & Non-payment of rent (transfer) & 0.02 & 0.13 & 40,727 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 57.81 & 78.29 & 39,087 \\
 & Case defaulted & 0.20 & 0.40 & 40,727 \\
 & Case involuntarily dismissed & 0.29 & 0.45 & 40,727 \\
 & Case heard & 0.06 & 0.23 & 40,727 \\
 & Case mediated & 0.41 & 0.49 & 40,727 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,727 \\
 & Plaintiff has an attorney & 0.84 & 0.37 & 40,727 \\
 & Defendant is an entity & 0.01 & 0.08 & 40,727 \\
 & Plaintiff is an entity & 0.70 & 0.46 & 40,727 \\
 & Money judgment & 1890.34 & 5279.49 & 40,727 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 9435708.78 & 20612629.31 & 14,491 \\
 & Building value & 2482603.38 & 6470958.91 & 14,491 \\
 & Land value & 113817.19 & 536568.37 & 14,491 \\
 & Other value & 12020146.88 & 26285935.89 & 14,491 \\
 & Units & 42.25 & 112.87 & 14,491 \\
\cline{1-5}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 261462.86 & 238040.64 & 9,842 \\
 & Four years before latest docket date & 280243.32 & 276051.45 & 9,968 \\
 & Three years before latest docket date & 307137.16 & 369763.53 & 10,172 \\
 & Two years before latest docket date & 341084.08 & 987145.51 & 10,182 \\
 & One year before latest docket date & 351172.05 & 311982.74 & 10,190 \\
 & Latest docket date & 377384.02 & 316645.29 & 10,096 \\
 & One year after latest docket date & 421601.75 & 344328.86 & 10,443 \\
 & Two years after latest docket date & 477948.08 & 457694.83 & 9,175 \\
 & Three years after latest docket date & 501611.80 & 780467.01 & 5,894 \\
\cline{1-5}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccc}
\toprule
 &  & Median & Mean & S.D. & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.00 & 0.12 & 0.32 & 40,727 \\
 & For cause (transfer) & 0.00 & 0.01 & 0.08 & 40,727 \\
 & Foreclosure & 0.00 & 0.02 & 0.14 & 40,727 \\
 & Foreclosure (transfer) & 0.00 & 0.00 & 0.03 & 40,727 \\
 & No cause & 0.00 & 0.10 & 0.30 & 40,727 \\
 & No cause (transfer) & 0.00 & 0.01 & 0.08 & 40,727 \\
 & Non-payment of rent & 1.00 & 0.73 & 0.44 & 40,727 \\
 & Non-payment of rent (transfer) & 0.00 & 0.02 & 0.13 & 40,727 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case duration & 21.00 & 57.81 & 78.29 & 39,087 \\
 & Case defaulted & 0.00 & 0.20 & 0.40 & 40,727 \\
 & Case involuntarily dismissed & 0.00 & 0.29 & 0.45 & 40,727 \\
 & Case heard & 0.00 & 0.06 & 0.23 & 40,727 \\
 & Case mediated & 0.00 & 0.41 & 0.49 & 40,727 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.00 & 0.09 & 0.28 & 40,727 \\
 & Plaintiff has an attorney & 1.00 & 0.84 & 0.37 & 40,727 \\
 & Defendant is an entity & 0.00 & 0.01 & 0.08 & 40,727 \\
 & Plaintiff is an entity & 1.00 & 0.70 & 0.46 & 40,727 \\
 & Money judgment & 0.00 & 1890.34 & 5279.49 & 40,727 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 775200.00 & 9435708.78 & 20612629.31 & 14,491 \\
 & Building value & 190000.00 & 2482603.38 & 6470958.91 & 14,491 \\
 & Land value & 2600.00 & 113817.19 & 536568.37 & 14,491 \\
 & Other value & 1067000.00 & 12020146.88 & 26285935.89 & 14,491 \\
 & Units & 1.00 & 42.25 & 112.87 & 14,491 \\
\cline{1-6}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 213270.60 & 261462.86 & 238040.64 & 9,842 \\
 & Four years before latest docket date & 225065.75 & 280243.32 & 276051.45 & 9,968 \\
 & Three years before latest docket date & 240097.38 & 307137.16 & 369763.53 & 10,172 \\
 & Two years before latest docket date & 259176.00 & 341084.08 & 987145.51 & 10,182 \\
 & One year before latest docket date & 278722.25 & 351172.05 & 311982.74 & 10,190 \\
 & Latest docket date & 305144.00 & 377384.02 & 316645.29 & 10,096 \\
 & One year after latest docket date & 347550.00 & 421601.75 & 344328.86 & 10,443 \\
 & Two years after latest docket date & 393900.00 & 477948.08 & 457694.83 & 9,175 \\
 & Three years after latest docket date & 414600.00 & 501611.80 & 780467.01 & 5,894 \\
\cline{1-6}
\bottomrule
\end{tabular}
